### 2017-02-01 abstract.tex
Corrections to Abstract and Intro

In the first experimental study, solar control of irregularity production is investigated using the Super Dual Auroral Radar Network (SuperDARN) radar at McMurdo, Antarctica.  The occurrence trends for irregularities are analyzed statistically and a model is developed that describes the location of radar echoes within the radar's field-of-view.  The trends are explained through variations in background density with solar illumination affecting radar beam propagation.  However, it is found that the irregularity occurrence during the night is higher than expected from ray tracing simulations based on a standard ionospheric density model.  The high occurrence at night implies an additional source of plasma density and it is proposed that large-scale density enhancements called polar patches may and be the source of this density.

@@

It is concluded from this body of work that the production of small-scale plasma irregularities in the polar \(F\)-region ionosphere is controlled both by global factors such as solar illumination as well as local plasma density gradients and electric fields.  In general, linear gradient-drift instability theory describes small-scale irregularity production well, particularly for low amplitude perturbations.  The production of irregularities is complex, and while ground-based radars are invaluable tools to study the ionosphere, care must be taken to interpret results correctly.

>>>>

In the first experimental study, solar control of irregularity production is investigated using the Super Dual Auroral Radar Network (SuperDARN) radar at McMurdo, Antarctica.  The occurrence trends for irregularities are analyzed statistically and a model is developed that describes the location of radar echoes within the radar's field-of-view.  The trends are explained through variations in background plasma density with solar illumination affecting radar beam propagation.  However, it is found that the irregularity occurrence during the night is higher than expected from ray tracing simulations based on a standard ionospheric density model.  The high occurrence at night implies an additional source of plasma density and it is proposed that large-scale density enhancements called polar patches may be the source of this density.

@@

It is concluded from this body of work that the production of small-scale plasma irregularities in the polar \(F\)-region ionosphere is controlled both by global factors such as solar illumination as well as local plasma density gradients and electric fields.  In general, linear gradient-drift instability theory describes small-scale irregularity production well, particularly for low-amplitude perturbations.  The production of irregularities is complex, and while ground-based radars are invaluable tools to study the ionosphere, care must be taken to interpret results correctly.
